---
title: "homework 5"
author: "Maelle Coupannec"
date: "17/11/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## LOADING LIBRARY

We are loading some library to clean the data and create the map.

```{r load library}
library(tidyverse)
library(forcats)
library(tigris)
library(viridis)
library(sf)
library(ggthemes)


```

# Reading And Cleaning The Data

First we read the data file which is in the data sub directory of the project file. Using `r fct_lump()` we only keep the three races with the highest number of homicides for that city, the rest are assigned to others and are filtered out. Finally, the disposition factor are reassigned to solved or unsolved for uniformity. 
 

```{r}
homicides <- read_csv("../data/homicide-data.csv")

homicides <- homicides %>%
  unite(col = city_name, c(city, state), sep=", ") %>%
  filter(city_name=="Las Vegas, NV") %>% 
  mutate(victim_race= fct_lump(victim_race, n=3)) %>% 
  filter(!is.na(lon)|!is.na(lon)) %>% 
  filter(victim_race!="Other") %>%
  mutate(disposition=fct_recode(disposition,
                                solved = "Closed by arrest",
                                unsolved = "Closed without arrest", 
                                unsolved ="Open/No arrest"))
  

head(homicides)
```

# Creation Of The Map

The map SF shape is downloaded from the Tigris package, it was chosen to upload the block contour of Clark county as boundaries for Las vegas geography. Points showing homicides were added on the map. Different facets for solved versus unsolved homicides and different colors to show the three race groups were used.


```{r}
map_lv <- block_groups( state="NV", county = "Clark county", 
                  year = NULL, class="sf")


ggplot()+
  geom_sf(data = map_lv, color = "black", 
          alpha = 0.1, size = 0.1)+
  geom_point(data = homicides, 
             aes(x = lon, y = lat, 
                shape = disposition, 
                color = victim_race), size = 0.8) +
  ggtitle("Homicides in Las Vegas, Nevada",
          subtitle = "Solved and unsolved casses by race")+
  labs(x = "", y = "", shape= "case status", 
       color= "race of the victim")

```
# Second Map Sowing only the city area

Since the first map shown the whole county and points where on top of each other, the geographic coordinate were restricted to the city area. 

```{r, fig.height=20, fig.width=10}
ggplot()+
  geom_sf(data = map_lv, color = "pink", 
          alpha = 0.1, size = 0.1)+
  geom_point(data = homicides, 
             aes(x = lon, y = lat, 
                shape = disposition, 
                color = victim_race), size = 0.8)+
  xlim(c(-115.4, -114.8)) + ylim(c(35.9, 36.4))+
  ggtitle("Homicides in Las Vegas, Nevada",
          subtitle = "Solved and unsolved casses by race")+
  theme_few() + 
  labs(x = "", y = "", shape= "case status", 
       color= "race of the victim")+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
  
```

